mouse level quality plots

### 2020-01-06 doc/MouseLevelPlots.Rmd
mouse level plots with batch18, add 3 mice to exclude list. updated data setup

#load main data file
load(file="data/MLH1/MLH1_data_setup_11.12.19.RData")#added batch17
#load(file="data/MLH1/MLH1_data_setup_9.26.19.RData")#added batch16
#load(file="data/MLH1/MLH1_data_setup_8.29.19.RData")#batch15 isn't showing up
#load(file="data/MetaData.RData")#this Rdata was replacing the most current batch.. agg!

>>>>

#load main data file
load(file="C:/Users/alpeterson7/Documents/MLH1repo/data/MLH1/MLH1_data_setup_1.5.20.RData")#added batch18
#load(file="data/MLH1/MLH1_data_setup_11.12.19.RData")#added batch17
#load(file="data/MLH1/MLH1_data_setup_9.26.19.RData")#added batch16
#load(file="data/MLH1/MLH1_data_setup_8.29.19.RData")#batch15 isn't showing up
#load(file="data/MetaData.RData")#this Rdata was replacing the most current batch.. agg!
